---
title: "Data Replication Project"
Author: "Salma Ghazi, Shana Mandelbaum"
output: 
  html_document:
    toc: yes
    code_folding: hide
date: "2024-06-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(tidyverse)
library(stargazer)
library(stm)

theme_set(theme_bw())
```

# Description
Replicated figure 4, table 3, figures 2 and 3, and table 4 from https://static1.squarespace.com/static/5ac4569925bf02b3f05a651f/t/638b509cb141756009541e29/1670074524751/Immigration_Paper_V2-1.pdf using only google trends data (without the bing portion)

# Replication

## Download Google Trends Data + Format

```{r}
reporting_data <- read_csv("Google_Trends_Immigrant_Reporting.csv") 
crime_data <- read_csv("Google_Trends_Immigrant_Crime.csv") 
welfare_data <- read_csv("Google_Trends_Immigrant_Welfare.csv") 


reporting_data <- 
  reporting_data %>% 
  rename(search_interest = Num_Searches) %>%
  mutate(date=parse_date(Month, "%Y-%m")) %>%
  filter(year(date) < 2020)


crime_data <- 
  crime_data %>% 
  rename(search_interest = Num_Searches) %>%
  mutate(date=parse_date(Month, "%Y-%m")) %>%
  filter(year(date) < 2020) %>%
  filter(search_interest != 0)


welfare_data <- 
  welfare_data %>% 
  rename(search_interest = Num_Searches) %>%
  mutate(date=parse_date(Month, "%Y-%m")) %>%
  filter(year(date) < 2020) %>%
  filter(search_interest != 0)

```


```{r}
reporting_data <- 
  reporting_data %>%
  mutate(President = ifelse(year(date) < 2009, "Bush", ifelse(year(date) < 2017, "Obama", "Trump")))

crime_data <- 
  crime_data %>%
  mutate(President = ifelse(year(date) < 2009, "Bush", ifelse(year(date) < 2017, "Obama", "Trump")))

welfare_data <- 
  welfare_data %>%
  mutate(President = ifelse(year(date) < 2009, "Bush", ifelse(year(date) < 2017, "Obama", "Trump")))
```


## Figure 4
```{r}
reporting_data %>%
  ggplot(aes(x = date, y = search_interest, color = President)) +
  geom_point() +
  geom_smooth(method = "lm", se = F) +
  labs(x = "Date", y = "Reporting Search Interest")

crime_data %>%
  ggplot(aes(x = date, y = search_interest, color = President)) +
  geom_point() +
  geom_smooth(method = "lm", se = F) +
  labs(x = "Date", y = "Crime Search Interest")


welfare_data %>%
  ggplot(aes(x = date, y = search_interest, color = President)) +
  geom_point() +
  geom_smooth(method = "lm", se=F) +
  labs(x = "Date", y = "Welfare Search Interest")
  

```

## Table 3 

```{r}
reporting_data <- 
  reporting_data %>%
  mutate(Is_Bush = (President=="Bush"), Is_Obama = (President=="Obama"), Is_Trump = (President=="Trump"))

crime_data <- 
  crime_data %>%
  mutate(Is_Bush = (President=="Bush"), Is_Obama = (President=="Obama"), Is_Trump = (President=="Trump"))

welfare_data <- 
  welfare_data %>%
  mutate(Is_Bush = (President=="Bush"), Is_Obama = (President=="Obama"), Is_Trump = (President=="Trump"))

```

```{r}
reporting_model <- lm(search_interest ~ date + Is_Bush + Is_Trump + Is_Obama , data=reporting_data)
crime_model <- lm(search_interest ~ date + Is_Bush + Is_Trump + Is_Obama , data=crime_data)
welfare_model <- lm(search_interest ~ date + Is_Bush + Is_Trump + Is_Obama , data=welfare_data)

stargazer(crime_model, welfare_model, reporting_model, type = "text",
          column.labels = c("Crime", "Welfare", "Report"))

```

We obtained different results than the paper due to differences in our data downloaded from google trends.
When given the exact data the paper used, we obtained their results

## Figures 2+3

Topics 1+3 for Crime
Topics 13 for Welfare

```{r}
load("topic_model_lite.RData")
```

Topic Model was given to us

```{r}
line_data <- 
  document_topics %>%
  group_by(time) %>%
  summarize(line_date = max(floor_date(ymd(date), "month")))


document_topics %>%
  mutate(month = floor_date(ymd(date), "month")) %>%
  group_by(month, channel, time) %>%
  summarize(num_segments = n()) %>%
  ggplot(aes(x = month, y = num_segments, color = channel)) +
  geom_point() +
  geom_smooth(aes(group = interaction(channel, time)), se = F) + 
  scale_color_manual(values = c("magenta", "red3", "blue")) + 
  geom_vline(data = line_data, aes(xintercept = line_date), linetype = "dashed") +
  labs(x = "Date", y = "Number of News Segments")
  
```
```{r}
#Crime Plot
document_topics %>%
  select(Topic1, Topic3, date, channel, time) %>%
  mutate(month = floor_date(ymd(date), "month")) %>%
  group_by(month, channel, time) %>%
  summarize(crime_prop = sum(Topic1, Topic3)) %>%
  ggplot(aes(x = month, y = crime_prop, color = channel)) +
  geom_point() +
  geom_smooth(aes(group = interaction(channel, time)), se = F) + 
  scale_color_manual(values = c("magenta", "red3", "blue")) + 
  geom_vline(data=line_data, aes(xintercept = line_date), linetype = "dashed") +
  labs(x = "Date", y = "Crime Proportion")


#Welfare Plot
document_topics %>%
  select(Topic13, date, channel, time) %>%
  mutate(month = floor_date(ymd(date), "month")) %>%
  group_by(month, channel, time) %>%
  summarize(welfare_prop = sum(Topic13)) %>%
  ggplot(aes(x = month, y = welfare_prop, color = channel)) +
  geom_point() + 
  geom_smooth(aes(group = interaction(channel, time)), se=F) + 
  scale_color_manual(values = c("magenta", "red3", "blue")) + 
  geom_vline(data = line_data, aes(xintercept = line_date), linetype = "dashed") +
  labs(x = "Date", y = "Welfare Proportion")
  
  
```

## Table 4

this model does not include the daily data

```{r}
Segment_Info <- 
  document_topics %>%
  mutate(month = floor_date(ymd(date), "month")) %>%
  group_by(month, channel, time) %>%
  summarize(num_segments = n(), welfare_prop = sum(Topic13), crime_prop = sum(Topic1, Topic3)) %>%
  mutate(month_of_year = month(month)) %>%
  inner_join(reporting_data, join_by(month == date)) 

table_4_model <- lm(search_interest ~ num_segments + welfare_prop + crime_prop + Is_Trump + month + month_of_year, data=Segment_Info)


stargazer(table_4_model, type = "text")
```

This model does include the daily data

```{r}
daily_info <- read_csv("gt_report_daily.csv")

Segment_Info_Daily <- 
  document_topics %>%
  mutate(Is_Trump = (date >= "2017-01-20")) %>%
  group_by(date, channel, time, Is_Trump) %>%
  mutate(date = as.Date(date, "%Y-%m-%d")) %>%
  summarize(num_segments = n(), welfare_prop = sum(Topic13), crime_prop = sum(Topic1, Topic3)) %>%
  mutate(month_of_year = as.factor(month(date)), day_of_week = as.factor(wday(date))) %>%
  inner_join(daily_info, join_by(date == date)) 

table_4_model_daily <- lm(search_adj ~ num_segments + welfare_prop + crime_prop + Is_Trump + date + month_of_year + day_of_week, data=Segment_Info_Daily)

stargazer(table_4_model_daily, type = "text")
```
# Extension

We are looking at the correlation between media coverage of the Mexican border crisis and migrants being apprehended and expelled at the border during the time period of 2014-2019.

## Download Border Data
```{r}
border_migrant_data <- read_csv("border_migrant_data.csv")
```
## Graph Border Apprehensions Over Time
```{r}
border_migrant_data <- border_migrant_data %>%  
  mutate(date = parse_date(Date, "%Y-%m")) %>% 
  mutate(president = ifelse(year(date) < 2017, "Obama", "Trump"))

border_migrant_data %>% 
  ggplot(aes(x = date, y = Number, color = president)) + 
  geom_point() +
  geom_smooth(se = F) + 
  labs(x = "Date", y = "Immigrants at Border")
```

## Media Coverage Graph

We are looking at Topic 6 as this is the topic that discusses the Mexican border crisis.

```{r}
document_topics %>% 
  mutate(month = floor_date(ymd(date), "month")) %>%  
  group_by(time, channel, month) %>% 
  summarise(border_prop = sum(Topic6)) %>% 
  ggplot(aes(x = month, y = border_prop, color = channel)) +
  geom_point() + 
  geom_smooth(aes(group = interaction(channel, time)), se = F) +
  scale_color_manual(values = c("magenta", "red3", "blue")) +
  geom_vline(data = line_data, aes(xintercept = line_date), linetype = "dashed") + 
  labs(x = "Date", y = "Border Proportion")
```

We can conclude from this that during the Trump administration the number of people being apprehended and expelled at the border increased, as did media coverage of the Mexican border crisis

## Graphs Mapped Together

```{r}
migrant_plot_data <- border_migrant_data %>% 
  filter(year(date) < 2020)
documents_plot_data <- document_topics %>% 
  filter(channel == "fox") %>% 
  mutate(month = floor_date(ymd(date), "month")) %>% 
  mutate(time = ifelse(date <= "2017-01-01", "pre", "post")) %>% 
  group_by(time, channel, month) %>% 
  summarise(border_prop = sum(Topic6))
 
line_plot_data <- line_data %>% 
  filter(line_date == "2017-01-01")
 
ggplot() +
  geom_point(data = migrant_plot_data, aes(x = date, y = Number, color = president)) +
  geom_smooth(data = migrant_plot_data, aes(x = date, y = Number, color = president), 
              se = FALSE) +
  scale_y_continuous(name = "Number", limits = c(0, 150000)) +
  geom_point(data = documents_plot_data,  aes(x = month, y = border_prop * 1500, group = time), 
             color = "blue") +
  geom_smooth(data = documents_plot_data, aes(x = month, y = border_prop * 1500, group = time), 
              se = FALSE, inherit.aes = FALSE) +
  geom_vline(data = line_plot_data, aes(xintercept = line_date), linetype = "dashed") +
  scale_y_continuous(
    name = "Immigrants at Border",
    limits = c(0, 150000),
    sec.axis = sec_axis(~./1500, name = "Border Proportion (Fox News)")
  ) +
  theme_minimal() + 
  theme(
    axis.title.y.right = element_text(color = "blue"),
    axis.text.y.right = element_text(color = "blue"),
    axis.ticks.y.right = element_line(color = "blue"))
```

We expected to see an obvious correlation between the number of migrants apprehended at the border and media coverage, but it seems to be the opposite.

## Regression

We did a regression to see if the proportion of times the border crisis was mentioned on the number of immigrants being apprehended on the border and the presidential administration.

```{r}
migrant_model_info <- document_topics %>% 
  mutate(Is_Trump = (date >= "2017-01-20")) %>% 
  group_by(channel, date, Is_Trump) %>% 
  mutate(date = as.Date(date, "%Y-%m-%d")) %>%  
  summarise(num_segs = n(), border_prop = sum(Topic6)) %>%  
  mutate(month_of_year = as.factor(month(date))) %>% 
  inner_join(border_migrant_data, join_by(date == date))
 
migrant_model <- lm(border_prop ~ Is_Trump + Number, data = migrant_model_info)
stargazer(migrant_model, type = "text", digits = 8)
```

Although we expected the number of immigrants apprehended at the border to have a larger effect than it did on the proportion of times the media discussed immigration at the border, this was not present in our regression. 

