---
title: "Data Replication Project"
Author: "Salma Ghazi, Shana Mandelbaum"
output: 
  html_document:
    toc: yes
date: "2024-06-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(tidyverse)
library(stargazer)

theme_set(theme_bw())
```

# Description
Replicated figure 4, table 3, figures 2 and 3, and table 4 from https://static1.squarespace.com/static/5ac4569925bf02b3f05a651f/t/638b509cb141756009541e29/1670074524751/Immigration_Paper_V2-1.pdf using only google trends data (without the bing portion)

# Replication

## Download Google Trends Data + Format

```{r}
reporting_data <- read_csv("Google_Trends_Immigrant_Reporting.csv") 
crime_data <- read_csv("Google_Trends_Immigrant_Crime.csv") 
welfare_data <- read_csv("Google_Trends_Immigrant_Welfare.csv") 


reporting_data <- 
  reporting_data %>% 
  rename(search_interest = Num_Searches) %>%
  mutate(date=parse_date(Month, "%Y-%m")) %>%
  filter(year(date) < 2020)


crime_data <- 
  crime_data %>% 
  rename(search_interest = Num_Searches) %>%
  mutate(date=parse_date(Month, "%Y-%m")) %>%
  filter(year(date) < 2020) %>%
  filter(search_interest != 0)


welfare_data <- 
  welfare_data %>% 
  rename(search_interest = Num_Searches) %>%
  mutate(date=parse_date(Month, "%Y-%m")) %>%
  filter(year(date) < 2020) %>%
  filter(search_interest != 0)

```


```{r}
reporting_data <- 
  reporting_data %>%
  mutate(President = ifelse(year(date) < 2009, "Bush", ifelse(year(date) < 2017, "Obama", "Trump")))

crime_data <- 
  crime_data %>%
  mutate(President = ifelse(year(date) < 2009, "Bush", ifelse(year(date) < 2017, "Obama", "Trump")))

welfare_data <- 
  welfare_data %>%
  mutate(President = ifelse(year(date) < 2009, "Bush", ifelse(year(date) < 2017, "Obama", "Trump")))
```


## Figure 4
```{r}
reporting_data %>%
  ggplot(aes(x = date, y = search_interest, color = President)) +
  geom_point() +
  geom_smooth(method = "lm", se = F)

crime_data %>%
  ggplot(aes(x = date, y = search_interest, color = President)) +
  geom_point() +
  geom_smooth(method = "lm", se = F)


welfare_data %>%
  ggplot(aes(x = date, y = search_interest, color = President)) +
  geom_point() +
  geom_smooth(method = "lm", se=F)
  

```

## Table 3 

```{r}
reporting_data <- 
  reporting_data %>%
  mutate(Is_Bush = (President=="Bush"), Is_Obama = (President=="Obama"), Is_Trump = (President=="Trump"))

crime_data <- 
  crime_data %>%
  mutate(Is_Bush = (President=="Bush"), Is_Obama = (President=="Obama"), Is_Trump = (President=="Trump"))

welfare_data <- 
  welfare_data %>%
  mutate(Is_Bush = (President=="Bush"), Is_Obama = (President=="Obama"), Is_Trump = (President=="Trump"))

```

```{r}
reporting_model <- lm(search_interest ~ date + Is_Bush + Is_Trump + Is_Obama , data=reporting_data)
crime_model <- lm(search_interest ~ date + Is_Bush + Is_Trump + Is_Obama , data=crime_data)
welfare_model <- lm(search_interest ~ date + Is_Bush + Is_Trump + Is_Obama , data=welfare_data)

stargazer(crime_model, welfare_model, reporting_model, type = "text",
          column.labels = c("Crime", "Welfare", "Report"))

```

We obtained different results than the paper due to differences in our data downloaded from google trends.
When given the exact data the paper used, we obtained their results

## Figures 2+3

Topics 1+3 for Crime
Topics 13 for Welfare

```{r}
library(stm)
load("TopicModel.RData")
document_topics <- make.dt(immigrFit, meta = out$meta)
topic_terms <- t(exp(immigrFit$beta$logbeta[[1]]))
rownames(topic_terms) <- out$vocab
colnames(topic_terms) <- sprintf("Topic%d", 1:ncol(topic_terms))
```

Topic Model was given to us

```{r}
line_data <- 
  document_topics %>%
  group_by(time) %>%
  summarize(line_date = max(floor_date(ymd(date), "month")))


document_topics %>%
  mutate(month = floor_date(ymd(date), "month")) %>%
  group_by(month, channel, time) %>%
  summarize(num_segments = n()) %>%
  ggplot(aes(x = month, y = num_segments, color = channel)) +
  geom_point() +
  geom_smooth(aes(group = interaction(channel, time)), se = F) + 
  scale_color_manual(values = c("magenta", "red3", "blue")) + 
  geom_vline(data = line_data, aes(xintercept = line_date), linetype = "dashed")
  
```
```{r}
#Crime Plot
document_topics %>%
  select(Topic1, Topic3, date, channel, time) %>%
  mutate(month = floor_date(ymd(date), "month")) %>%
  group_by(month, channel, time) %>%
  summarize(crime_prop = sum(Topic1, Topic3)) %>%
  ggplot(aes(x = month, y = crime_prop, color = channel)) +
  geom_point() +
  geom_smooth(aes(group = interaction(channel, time)), se = F) + 
  scale_color_manual(values = c("magenta", "red3", "blue")) + 
  geom_vline(data=line_data, aes(xintercept = line_date), linetype = "dashed")


#Welfare Plot
document_topics %>%
  select(Topic13, date, channel, time) %>%
  mutate(month = floor_date(ymd(date), "month")) %>%
  group_by(month, channel, time) %>%
  summarize(welfare_prop = sum(Topic13)) %>%
  ggplot(aes(x = month, y = welfare_prop, color = channel)) +
  geom_point() + 
  geom_smooth(aes(group = interaction(channel, time)), se=F) + 
  scale_color_manual(values = c("magenta", "red3", "blue")) + 
  geom_vline(data = line_data, aes(xintercept = line_date), linetype = "dashed")
  
  
```

## Table 4

this model does not include the daily data

```{r}
Segment_Info <- 
  document_topics %>%
  mutate(month = floor_date(ymd(date), "month")) %>%
  group_by(month, channel, time) %>%
  summarize(num_segments = n(), welfare_prop = sum(Topic13), crime_prop = sum(Topic1, Topic3)) %>%
  mutate(month_of_year = month(month)) %>%
  inner_join(reporting_data, join_by(month == date)) 

table_4_model <- lm(search_interest ~ num_segments + welfare_prop + crime_prop + Is_Trump + month + month_of_year, data=Segment_Info)


stargazer(table_4_model, type = "text")
```

This model does include the daily data

```{r}
daily_info <- read_csv("gt_report_daily.csv")

Segment_Info_Daily <- 
  document_topics %>%
  mutate(Is_Trump = (date >= "2017-01-20")) %>%
  group_by(date, channel, time, Is_Trump) %>%
  mutate(date = as.Date(date, "%Y-%m-%d")) %>%
  summarize(num_segments = n(), welfare_prop = sum(Topic13), crime_prop = sum(Topic1, Topic3)) %>%
  mutate(month_of_year = as.factor(month(date)), day_of_week = as.factor(wday(date))) %>%
  inner_join(daily_info, join_by(date == date)) 

table_4_model_daily <- lm(search_adj ~ num_segments + welfare_prop + crime_prop + Is_Trump + date + month_of_year + day_of_week, data=Segment_Info_Daily)

stargazer(table_4_model_daily, type = "text")
```
# Extension

We decided to examine this claim in the paper: "While there was a significant increase in negative coverage of immigrants after Trump’s inauguration, the Trump administration also engaged in substantial anti-immigrant messaging and policy initiatives"
To do this, we are looking at the association between media coverage of the border crisis and data of how many people were apprehended or expelled at the Mexican border.

## Download Border Data
```{r}
border_migrant_data <- read_csv("border_migrant_data.csv")
```
## Graph border apprehensions over time
```{r}
border_migrant_data <- border_migrant_data %>%  
  mutate(date = parse_date(Date, "%Y-%m")) %>% 
  mutate(president = ifelse(year(date) < 2017, "Obama", "Trump"))

border_migrant_data %>% 
  ggplot(aes(x = date, y = Number, color = president)) + 
  geom_point() +
  geom_smooth(se = F)
```

## Media Coverage Graph

We are looking at Topic 6 as this is the topic that discusses the Mexican border crisis.

```{r}
document_topics %>% 
  mutate(month = floor_date(ymd(date), "month")) %>%  
  group_by(time, channel, month) %>% 
  summarise(border_prop = sum(Topic6)) %>% 
  ggplot(aes(x = month, y = border_prop, color = channel)) +
  geom_point() + 
  geom_smooth(aes(group = interaction(channel, time)), se = F) +
  scale_color_manual(values = c("magenta", "red3", "blue")) +
  geom_vline(data = line_data, aes(xintercept = line_date), linetype = "dashed")
```

We can conclude from this that during the Trump administration the number of people being apprehended and expelled at the border increased, as did media coverage of the Mexican border crisis
